---
title: "auditor"
date: "`r format(Sys.time(), '%d-%m-%Y')`"
output:
  html_document:
    toc: true
    toc_float: true
---

  
This report aims to present the capabilities of the package `auditor`. 

The document contains a use-case of on the [titanic_imputed](https://modeloriented.github.io/DALEX/reference/titanic.html) data set described in Section real-world use-case of the article.

We did our best to show the entire range of the implemented explanations. Please note that the examples may be incomplete. If you think something is missing, feel free to make a pull request at the GitHub repository [MI2DataLab/IML-tools](https://github.com/MI2DataLab/IML-tools)

The document is a part of the paper "Landscape of R packages for ExplainableMachine Learning", S. Maksymiuk, A. Gosiewska, and P. Biecek. 
The list of use-cases for all packages included in the article is [here](https://mi2datalab.github.io/IML-tools/).  
  
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE, warning = FALSE)
```



Load [`titanic_imputed`](https://modeloriented.github.io/DALEX/reference/titanic.html) data set.

```{r}
data(titanic_imputed, package = "DALEX")

head(titanic_imputed)
```

```{r}
library(auditor)
library(randomForest)
```


Fit a forest type model to the titanic imputed data.

```{r}
rf_model <- randomForest::randomForest(as.factor(survived)~., data = titanic_imputed)
gbm_model <- gbm::gbm(survived~., data = titanic_imputed, distribution = "bernoulli")
```

# Model Diagnostics

## Half-normal plots


```{r}
exp <- DALEX::explain(rf_model, data = titanic_imputed, y = titanic_imputed$survived, verbose = FALSE)
hf <- model_halfnormal(exp)
plot_halfnormal(hf)
```


## LIFT curve - One model

```{r}
exp <- DALEX::explain(rf_model, data = titanic_imputed, y = titanic_imputed$survived, verbose = FALSE)
eva_rf <- model_evaluation(exp)
plot(eva_rf, type = "lift")
```

## LIFT curve - Two models

```{r}
exp_rf <- DALEX::explain(rf_model, data = titanic_imputed, y = titanic_imputed$survived, verbose = FALSE)
exp_gbm <- DALEX::explain(gbm_model, data = titanic_imputed, y = titanic_imputed$survived, verbose = FALSE)
eva_rf <- model_evaluation(exp_rf)
eva_gbm <- model_evaluation(exp_gbm)
plot(eva_gbm, eva_rf, type = "lift")
```

## Observed vs Predicted - One model

```{r}
exp <- DALEX::explain(rf_model, data = titanic_imputed, y = titanic_imputed$survived, verbose = FALSE)
res_rf <- model_residual(exp)
plot(res_rf, type = "prediction")
```

## Observed vs Predicted - Two models

```{r}
exp_rf <- DALEX::explain(rf_model, data = titanic_imputed, y = titanic_imputed$survived, verbose = FALSE)
exp_gbm <- DALEX::explain(gbm_model, data = titanic_imputed, y = titanic_imputed$survived, verbose = FALSE)
res_rf <- model_residual(exp_rf)
res_gbm <- model_residual(exp_gbm)
plot(res_gbm, res_rf, type = "prediction")
```

## Variable vs Predicted - One model

```{r}
exp <- DALEX::explain(rf_model, data = titanic_imputed, y = titanic_imputed$survived, verbose = FALSE)
res_rf <- model_residual(exp)
plot(res_rf, type = "prediction", variable = "fare")
```

## Variable vs Predicted - Two models

```{r}
exp_rf <- DALEX::explain(rf_model, data = titanic_imputed, y = titanic_imputed$survived, verbose = FALSE)
exp_gbm <- DALEX::explain(gbm_model, data = titanic_imputed, y = titanic_imputed$survived, verbose = FALSE)
res_rf <- model_residual(exp_rf)
res_gbm <- model_residual(exp_gbm)
plot(res_gbm, res_rf, type = "prediction", variable = "fare")
```

## Density of residuals - One model

```{r}
exp <- DALEX::explain(rf_model, data = titanic_imputed, y = titanic_imputed$survived, verbose = FALSE)
res_rf <- model_residual(exp)
plot(res_rf, type = "residual_density")
```

## Correlation of models

```{r}
exp_rf <- DALEX::explain(rf_model, data = titanic_imputed, y = titanic_imputed$survived, verbose = FALSE)
exp_gbm <- DALEX::explain(gbm_model, data = titanic_imputed, y = titanic_imputed$survived, verbose = FALSE)
res_rf <- model_residual(exp_rf)
res_gbm <- model_residual(exp_gbm)
plot(res_gbm, res_rf, type = "correlation")
```




