---
title: "DALEXtra"
date: "`r format(Sys.time(), '%d-%m-%Y')`"
output:
  html_document:
    toc: true
    toc_float: true
---

  
This report aims to present the capabilities of the package `DALEXtra`. 

The document contains a use-case of on the [titanic_imputed](https://modeloriented.github.io/DALEX/reference/titanic.html) data set described in Section real-world use-case of the article.

We did our best to show the entire range of the implemented explanations. Please note that the examples may be incomplete. If you think something is missing, feel free to make a pull request at the GitHub repository [MI2DataLab/IML-tools](https://github.com/MI2DataLab/IML-tools)

The document is a part of the paper "Landscape of R packages for ExplainableMachine Learning", S. Maksymiuk, A. Gosiewska, and P. Biecek. 
The list of use-cases for all packages included in the article is [here](https://mi2datalab.github.io/IML-tools/).  

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE, warning = FALSE)
```

Load [`titanic_imputed`](https://modeloriented.github.io/DALEX/reference/titanic.html) data set.

```{r}
data(titanic_imputed, package = "DALEX")

head(titanic_imputed)
```

Fit a forest type model and logistic regression to the titanic imputed data.

```{r}
ranger_model <- ranger::ranger(survived~., data = titanic_imputed, classification = TRUE, probability = TRUE)
gbm_model <- gbm::gbm(survived~., data = titanic_imputed, distribution = "bernoulli")
```


```{r}
library(DALEXtra)
```

# Model Diagnostics

## Funnel Plot

```{r}
explainer_ranger <- explain(ranger_model, data = titanic_imputed, y = titanic_imputed$survived, label = "Ranger Model")
explainer_gbm <- explain(gbm_model, data = titanic_imputed, y = titanic_imputed$survived, label = "GBM Model")

fm <- funnel_measure(explainer_gbm, explainer_ranger, show_info = FALSE)
plot(fm)
```

## Overall comaprison

```{r}
explainer_ranger <- explain(ranger_model, data = titanic_imputed, y = titanic_imputed$survived, label = "Ranger Model", verbose = FALSE)
explainer_gbm <- explain(gbm_model, data = titanic_imputed, y = titanic_imputed$survived, label = "GBM Model", verbose = FALSE)

oc <- overall_comparison(explainer_gbm, explainer_ranger, type = "classification")
plot(oc)
```


## Training test comparison



```{r}
ind <- sample(1:nrow(titanic_imputed), 0.7*nrow(titanic_imputed))
train <- titanic_imputed[ind,]
test <- titanic_imputed[-ind,]

ranger_model <- ranger::ranger(survived~., data = train, classification = TRUE, probability = TRUE)
gbm_model <- gbm::gbm(survived~., data = train, distribution = "bernoulli")

explainer_ranger <- explain(ranger_model, data = test, y = test$survived, label = "Ranger Model", verbose = FALSE)
explainer_gbm <- explain(gbm_model, data = test, y = test$survived, label = "GBM Model", verbose = FALSE)

tt <- training_test_comparison(explainer_gbm, explainer_ranger, training_data = train, training_y = train$survived)
plot(tt)
```

# Report

Compiled report can be seen under this link: [https://mi2datalab.github.io/IML-tools/DALEXtra_champion_challenger.html](https://mi2datalab.github.io/IML-tools/DALEXtra_champion_challenger.html).

```{r eval = FALSE}
explainer_ranger <- explain(ranger_model, data = titanic_imputed, y = titanic_imputed$survived, label = "Ranger Model")
explainer_gbm <- explain(gbm_model, data = titanic_imputed, y = titanic_imputed$survived, label = "GBM Model")

fm <- funnel_measure(explainer_gbm, explainer_ranger, show_info = FALSE)

explainer_ranger <- explain(ranger_model, data = titanic_imputed, y = titanic_imputed$survived, label = "Ranger Model", verbose = FALSE)
explainer_gbm <- explain(gbm_model, data = titanic_imputed, y = titanic_imputed$survived, label = "GBM Model", verbose = FALSE)

oc <- overall_comparison(explainer_gbm, explainer_ranger, type = "classification")

ind <- sample(1:nrow(titanic_imputed), 0.7*nrow(titanic_imputed))
train <- titanic_imputed[ind,]
test <- titanic_imputed[-ind,]

ranger_model <- ranger::ranger(survived~., data = train, classification = TRUE, probability = TRUE)
gbm_model <- gbm::gbm(survived~., data = train, distribution = "bernoulli")

explainer_ranger <- explain(ranger_model, data = test, y = test$survived, label = "Ranger Model", verbose = FALSE)
explainer_gbm <- explain(gbm_model, data = test, y = test$survived, label = "GBM Model", verbose = FALSE)

tt <- training_test_comparison(explainer_gbm, explainer_ranger, training_data = train, training_y = train$survived)

champion_challenger(list(fm, oc, tt), title = "DALEXtra: Champion - Challenger analysis", author = "Szymon Maksymiuk", model_performance_table = TRUE, output_name = "DALEXtra_champion_challenger")
```



