---
title: "DALEX"
date: "`r format(Sys.time(), '%d-%m-%Y')`"
output:
  html_document:
    toc: true
    toc_float: true
---

  
This report aims to present the capabilities of the package `DALEX`. 

The document contains a use-case of on the [titanic_imputed](https://modeloriented.github.io/DALEX/reference/titanic.html) data set described in Section real-world use-case of the article.

We did our best to show the entire range of the implemented explanations. Please note that the examples may be incomplete. If you think something is missing, feel free to make a pull request at the GitHub repository [MI2DataLab/IML-tools](https://github.com/MI2DataLab/IML-tools)

The document is a part of the paper "Landscape of R packages for ExplainableMachine Learning", S. Maksymiuk, A. Gosiewska, and P. Biecek. 
The list of use-cases for all packages included in the article is [here](https://mi2datalab.github.io/IML-tools/).  


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE, warning = FALSE)
```



Load [`titanic_imputed`](https://modeloriented.github.io/DALEX/reference/titanic.html) data set.

```{r}
data(titanic_imputed, package = "DALEX")

head(titanic_imputed)
```


```{r}
library(DALEX)
```

Fit a random forest to the titanic imputed data.

```{r}
ranger_model <- ranger::ranger(survived~., data = titanic_imputed, classification = TRUE, probability = TRUE)
gbm_model <- gbm::gbm(survived~., data = titanic_imputed, distribution = "bernoulli")
```

# Model parts

## Variable importance

```{r}
explainer_ranger <- explain(ranger_model, data = titanic_imputed, y = titanic_imputed$survived, label = "Ranger Model")

fi_ranger <- model_parts(explainer_ranger)
plot(fi_ranger)
```


# Model Profile

## ALE Plot - One model

```{r}
explainer_ranger <- explain(ranger_model, data = titanic_imputed, y = titanic_imputed$survived, label = "Ranger Model", verbose = FALSE)

ale_ranger <- model_profile(explainer_ranger, variables = "fare", type = "accumulated")
plot(ale_ranger)
```

## ALE Plot - Two models

```{r}
explainer_ranger <- explain(ranger_model, data = titanic_imputed, y = titanic_imputed$survived, label = "Ranger Model", verbose = FALSE)
explainer_gbm <- explain(gbm_model, data = titanic_imputed, y = titanic_imputed$survived, label = "GBM Model", verbose = FALSE)

ale_ranger <- model_profile(explainer_ranger, variables = "fare", type = "accumulated")
ale_gbm <- model_profile(explainer_gbm, variables = "fare", type = "accumulated")
plot(ale_ranger$agr_profiles, ale_gbm$agr_profiles)
```

## PDP Plot - One model

```{r}
explainer_ranger <- explain(ranger_model, data = titanic_imputed, y = titanic_imputed$survived, label = "Ranger Model", verbose = FALSE)

pdp_ranger <- model_profile(explainer_ranger, variables = "fare", type = "partial")
plot(pdp_ranger)
```

## PDP Plot - Two models

```{r}
explainer_ranger <- explain(ranger_model, data = titanic_imputed, y = titanic_imputed$survived, label = "Ranger Model", verbose = FALSE)
explainer_gbm <- explain(gbm_model, data = titanic_imputed, y = titanic_imputed$survived, label = "GBM Model", verbose = FALSE)

pdp_ranger <- model_profile(explainer_ranger, variables = "fare", type = "partial")
pdp_gbm <- model_profile(explainer_gbm, variables = "fare", type = "partial")
plot(pdp_ranger$agr_profiles, pdp_gbm$agr_profiles)
```

## CDP Plot - One model

```{r}
explainer_ranger <- explain(ranger_model, data = titanic_imputed, y = titanic_imputed$survived, label = "Ranger Model", verbose = FALSE)

cdp_ranger <- model_profile(explainer_ranger, variables = "fare", type = "conditional")
plot(cdp_ranger)
```

## CDP Plot - Two models

```{r}
explainer_ranger <- explain(ranger_model, data = titanic_imputed, y = titanic_imputed$survived, label = "Ranger Model", verbose = FALSE)
explainer_gbm <- explain(gbm_model, data = titanic_imputed, y = titanic_imputed$survived, label = "GBM Model", verbose = FALSE)

cdp_ranger <- model_profile(explainer_ranger, variables = "fare", type = "conditional")
cdp_gbm <- model_profile(explainer_gbm, variables = "fare", type = "conditional")
plot(cdp_ranger$agr_profiles, cdp_gbm$agr_profiles)
```


# Model Diagnostics

## Residual plots - One model


```{r}
explainer_ranger <- explain(ranger_model, data = titanic_imputed, y = titanic_imputed$survived, label = "Ranger Model", verbose = FALSE)

md_ranger <- model_diagnostics(explainer_ranger)
plot(md_ranger)
```

```{r}
explainer_ranger <- explain(ranger_model, data = titanic_imputed, y = titanic_imputed$survived, label = "Ranger Model", verbose = FALSE)

md_ranger <- model_diagnostics(explainer_ranger)
plot(md_ranger, variable = "fare")
```

## Residual plots - Two models


```{r}
explainer_ranger <- explain(ranger_model, data = titanic_imputed, y = titanic_imputed$survived, label = "Ranger Model", verbose = FALSE)
explainer_gbm <- explain(gbm_model, data = titanic_imputed, y = titanic_imputed$survived, label = "GBM Model", verbose = FALSE)

md_ranger <- model_diagnostics(explainer_ranger)
md_gbm <- model_diagnostics(explainer_gbm)
plot(md_ranger, md_gbm)
```

```{r}
explainer_ranger <- explain(ranger_model, data = titanic_imputed, y = titanic_imputed$survived, label = "Ranger Model", verbose = FALSE)
explainer_gbm <- explain(gbm_model, data = titanic_imputed, y = titanic_imputed$survived, label = "GBM Model", verbose = FALSE)

md_ranger <- model_diagnostics(explainer_ranger)
md_gbm <- model_diagnostics(explainer_gbm)
plot(md_ranger, md_gbm, variable = "fare")
```

# Predict Parts

## BreakDown

```{r}
explainer_ranger <- explain(ranger_model, data = titanic_imputed, y = titanic_imputed$survived, label = "Ranger Model", verbose = FALSE)

bd_ranger <- predict_parts(explainer_ranger, new_observation = titanic_imputed[1,])
plot(bd_ranger)
```

## Oscillations

```{r}
explainer_ranger <- explain(ranger_model, data = titanic_imputed, y = titanic_imputed$survived, label = "Ranger Model", verbose = FALSE)

osc_ranger <- predict_parts(explainer_ranger, new_observation = titanic_imputed[1,], type = "oscillations")
plot(osc_ranger)
```

## shap

```{r}
explainer_ranger <- explain(ranger_model, data = titanic_imputed, y = titanic_imputed$survived, label = "Ranger Model", verbose = FALSE)

shap_ranger <- predict_parts(explainer_ranger, new_observation = titanic_imputed[1,], type = "shap")
plot(shap_ranger)
```

# Predict Profile

## Ceteris Paribus (ICE) - One model

```{r}
explainer_ranger <- explain(ranger_model, data = titanic_imputed, y = titanic_imputed$survived, label = "Ranger Model", verbose = FALSE)

cp_ranger <- predict_profile(explainer_ranger, new_observation = titanic_imputed[1,])
plot(cp_ranger)
```

## Ceteris Paribus (ICE) - Two models

```{r}
explainer_ranger <- explain(ranger_model, data = titanic_imputed, y = titanic_imputed$survived, label = "Ranger Model", verbose = FALSE)
explainer_gbm <- explain(gbm_model, data = titanic_imputed, y = titanic_imputed$survived, label = "GBM Model", verbose = FALSE)

cp_ranger <- predict_profile(explainer_ranger, new_observation = titanic_imputed[1,])
cp_gbm <- predict_profile(explainer_gbm, new_observation = titanic_imputed[1,])
plot(cp_ranger, cp_gbm)
```

# Predict Diagnostics

## Residual Diagnostics

```{r}
explainer_ranger <- explain(ranger_model, data = titanic_imputed, y = titanic_imputed$survived, label = "Ranger Model", verbose = FALSE)

rd_ranger <- predict_diagnostics(explainer_ranger, new_observation = titanic_imputed[1,], neighbors = 25)
plot(rd_ranger)
```
## Stability plots

```{r}
explainer_ranger <- explain(ranger_model, data = titanic_imputed, y = titanic_imputed$survived, label = "Ranger Model", verbose = FALSE)

sp_ranger <- predict_diagnostics(explainer_ranger, new_observation = titanic_imputed[1,], neighbors = 25, variables = c("fare", "age"))
plot(sp_ranger)
```

