---
title: "The fastshap R package"
date: "`r format(Sys.time(), '%d-%m-%Y')`"
output:
  html_document:
    toc: true
    toc_float: true
---

  
This report aims to present the capabilities of the package `fastshap`. 

The document is a part of the paper "Landscape of R packages for eXplainable Machine Learning", S. Maksymiuk, A. Gosiewska, and P. Biecek. 
(https://arxiv.org/abs/2009.13248). It contains a real life use-case with a hand of [titanic_imputed](https://modeloriented.github.io/DALEX/reference/titanic.html) data set described in Section *Example gallery for XAI packages* of the article.

We did our best to show the entire range of the implemented explanations. Please note that the examples may be incomplete. If you think something is missing, feel free to make a pull request at the GitHub repository [MI2DataLab/XAI-tools](https://github.com/MI2DataLab/XAI-tools).

The list of use-cases for all packages included in the article is [here](http://xai-tools.drwhy.ai/).  
  
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE, warning = FALSE)
```



Load [`titanic_imputed`](https://modeloriented.github.io/DALEX/reference/titanic.html) data set.

```{r}
data(titanic_imputed, package = "DALEX")

head(titanic_imputed)
```

```{r}
library(fastshap)
```


Fit a forest type model to the titanic imputed data.

```{r}
ranger_model <- ranger::ranger(survived~., data = titanic_imputed, classification = TRUE, probability = TRUE)
```

# Model Parts

## Shapley based feature importance


```{r}
pred_fun <- function(X.model, newdata) {
  predict(X.model, newdata)$predictions[,2]
}

shap <- explain(ranger_model, X = titanic_imputed, pred_wrapper = pred_fun, nsim = 50)
library(ggplot2)
autoplot(shap)
```

# Model Profile

## shap based dependence plot

```{r}
pred_fun <- function(X.model, newdata) {
  predict(X.model, newdata)$predictions[,2]
}

shap <- explain(ranger_model, X = titanic_imputed, pred_wrapper = pred_fun, nsim = 50)
library(ggplot2)
autoplot(shap, type = "dependence", feature = "fare", X = titanic_imputed, smooth = TRUE)
```



# Predict Parts

## shap based contributions

### R plots

```{r}
pred_fun <- function(X.model, newdata) {
  predict(X.model, newdata)$predictions[,2]
}

shap <- explain(ranger_model, X = titanic_imputed, pred_wrapper = pred_fun, nsim = 50)
library(ggplot2)
autoplot(shap, type = "contribution", row_num = 1)
```

### Python imported plots

Those plots were comupted with a hand of the `reticulate` package.


```{r}
pred_fun <- function(X.model, newdata) {
  predict(X.model, newdata)$predictions[,2]
}

shap <- explain(ranger_model, X = titanic_imputed, pred_wrapper = pred_fun, nsim = 50)

force_plot(shap[1,], baseline = mean(pred_fun(ranger_model, titanic_imputed)), feature_values = titanic_imputed[1,], display = "html")
```

# Session info

```{r}
sessionInfo()
```

