---
title: "flashlight"
date: "`r format(Sys.time(), '%d-%m-%Y')`"
output:
  html_document:
    toc: true
    toc_float: true
---

  
This report aims to present the capabilities of the package `flashlight` 

The document contains a use-case of on the [titanic_imputed](https://modeloriented.github.io/DALEX/reference/titanic.html) data set described in Section real-world use-case of the article.

We did our best to show the entire range of the implemented explanations. Please note that the examples may be incomplete. If you think something is missing, feel free to make a pull request at the GitHub repository [MI2DataLab/XAI-tools](https://github.com/MI2DataLab/XAI-tools)

The document is a part of the paper "Landscape of R packages for ExplainableMachine Learning", S. Maksymiuk, A. Gosiewska, and P. Biecek. 
The list of use-cases for all packages included in the article is [here](https://mi2datalab.github.io/XAI-tools/).  
  
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE, warning = FALSE)
```



Load [`titanic_imputed`](https://modeloriented.github.io/DALEX/reference/titanic.html) data set.

```{r}
data(titanic_imputed, package = "DALEX")

head(titanic_imputed)
```

```{r}
library(flashlight)
library(MetricsWeighted)
```


Fit a forest type model and decision tree to the titanic imputed data. 

```{r}
ranger_model <- ranger::ranger(survived~., data = titanic_imputed, classification = TRUE, probability = TRUE)
tree_model <- rpart::rpart(as.factor(survived)~., data = titanic_imputed)
```

# Model Parts

## Permutation feature importance - One model

```{r}
custom_predict <- function(X.model, new_data) {
  predict(X.model, new_data)$predictions[,1]
}
fl <- flashlight(model = ranger_model, data = titanic_imputed, y = "survived", label = "Titanic Ranger",
                 metrics = list(auc = AUC), predict_function = custom_predict)
imp <- light_importance(fl, m_repetitions = 10)
plot(imp, fill = "darkred")
```

## Permutation feature importance - Two models

```{r}
custom_predict_ranger <- function(X.model, new_data) {
  predict(X.model, new_data)$predictions[,1]
}

custom_predict_rpart <- function(X.model, new_data) {
  predict(X.model, new_data)[,1]
}

fl_ranger <- flashlight(model = ranger_model,  label = "Titanic Ranger",
                 metrics = list(auc = AUC), predict_function = custom_predict_ranger)

fl_rpart <- flashlight(model = tree_model,  label = "Titanic Tree",
                 metrics = list(auc = AUC), predict_function = custom_predict_rpart)

fl <- multiflashlight(list(fl_ranger, fl_rpart), data = titanic_imputed, y = "survived")

imp <- light_importance(fl, m_repetitions = 10)
plot(imp, fill = "darkred")
```

## Interactions - One model

```{r}
custom_predict <- function(X.model, new_data) {
  predict(X.model, new_data)$predictions[,1]
}
fl <- flashlight(model = ranger_model, data = titanic_imputed, y = "survived", label = "Titanic Ranger",
                 metrics = list(auc = AUC), predict_function = custom_predict)
st_1 <- light_interaction(fl, seed = 123)
plot(st_1, fill = "darkred")
```

## Interactions - TWo model

```{r}
custom_predict_ranger <- function(X.model, new_data) {
  predict(X.model, new_data)$predictions[,1]
}

custom_predict_rpart <- function(X.model, new_data) {
  predict(X.model, new_data)[,1]
}

fl_ranger <- flashlight(model = ranger_model,  label = "Titanic Ranger",
                 metrics = list(auc = AUC), predict_function = custom_predict_ranger)

fl_rpart <- flashlight(model = tree_model,  label = "Titanic Tree",
                 metrics = list(auc = AUC), predict_function = custom_predict_rpart)

fl <- multiflashlight(list(fl_ranger, fl_rpart), data = titanic_imputed, y = "survived")

st_2 <- light_interaction(fl, seed = 123)
plot(st_2, fill = "darkred")
```


## Pairwise Interactions - One model

```{r}
custom_predict <- function(X.model, new_data) {
  predict(X.model, new_data)$predictions[,1]
}
fl <- flashlight(model = ranger_model, data = titanic_imputed, y = "survived", label = "Titanic Ranger",
                 metrics = list(auc = AUC), predict_function = custom_predict)
st_1 <- light_interaction(fl, seed = 123)
stp <- light_interaction(fl, seed = 123, v = most_important(st_1, 4), pairwise = TRUE)
plot(stp, fill = "darkred")
```

## Interactions - TWo model

```{r}
custom_predict_ranger <- function(X.model, new_data) {
  predict(X.model, new_data)$predictions[,1]
}

custom_predict_rpart <- function(X.model, new_data) {
  predict(X.model, new_data)[,1]
}

fl_ranger <- flashlight(model = ranger_model,  label = "Titanic Ranger",
                 metrics = list(auc = AUC), predict_function = custom_predict_ranger)

fl_rpart <- flashlight(model = tree_model,  label = "Titanic Tree",
                 metrics = list(auc = AUC), predict_function = custom_predict_rpart)

fl <- multiflashlight(list(fl_ranger, fl_rpart), data = titanic_imputed, y = "survived")
st_2 <- light_interaction(fl, seed = 123)

stp <- light_interaction(fl, seed = 123, v = most_important(st_2, 4), pairwise = TRUE)
plot(stp, fill = "darkred")
```


# Model Profile

## ALE Plot - One model


```{r}
custom_predict <- function(X.model, new_data) {
  predict(X.model, new_data)$predictions[,1]
}
fl <- flashlight(model = ranger_model, data = titanic_imputed, y = "survived", label = "Titanic Ranger",
                 metrics = list(auc = AUC), predict_function = custom_predict)

ale <- light_profile(fl, v = "fare", type = "ale")
plot(ale)
```
## ALE Plot - Two models


```{r}
custom_predict_ranger <- function(X.model, new_data) {
  predict(X.model, new_data)$predictions[,1]
}

custom_predict_rpart <- function(X.model, new_data) {
  predict(X.model, new_data)[,1]
}

fl_ranger <- flashlight(model = ranger_model,  label = "Titanic Ranger",
                 metrics = list(auc = AUC), predict_function = custom_predict_ranger)

fl_rpart <- flashlight(model = tree_model,  label = "Titanic Tree",
                 metrics = list(auc = AUC), predict_function = custom_predict_rpart)

fl <- multiflashlight(list(fl_ranger, fl_rpart), data = titanic_imputed, y = "survived")

ale <- light_profile(fl, v = "fare", type = "ale")
plot(ale)
```

## Partial Dependence Plot - One model

```{r}
custom_predict <- function(X.model, new_data) {
  predict(X.model, new_data)$predictions[,2]
}
fl <- flashlight(model = ranger_model, data = titanic_imputed, y = "survived", label = "Titanic Ranger",
                 metrics = list(auc = AUC), predict_function = custom_predict)

pdp <- light_profile(fl, v = "fare", type = "partial dependence")
plot(pdp)
```

## Partial Dependence Plot - Two models

```{r}
custom_predict_ranger <- function(X.model, new_data) {
  predict(X.model, new_data)$predictions[,2]
}

custom_predict_rpart <- function(X.model, new_data) {
  predict(X.model, new_data)[,1]
}

fl_ranger <- flashlight(model = ranger_model,  label = "Titanic Ranger",
                 metrics = list(auc = AUC), predict_function = custom_predict_ranger)

fl_rpart <- flashlight(model = tree_model,  label = "Titanic Tree",
                 metrics = list(auc = AUC), predict_function = custom_predict_rpart)

fl <- multiflashlight(list(fl_ranger, fl_rpart), data = titanic_imputed, y = "survived")

pdp <- light_profile(fl, v = "fare", type = "partial dependence")
plot(pdp)
```
## Predicted value profile - One model

```{r}
custom_predict <- function(X.model, new_data) {
  predict(X.model, new_data)$predictions[,2]
}
fl <- flashlight(model = ranger_model, data = titanic_imputed, y = "survived", label = "Titanic Ranger",
                 metrics = list(auc = AUC), predict_function = custom_predict)

pvp <- light_profile(fl, v = "fare", type = "predicted")
plot(pvp)
```

## Predicted value profile - Two models

```{r}
custom_predict_ranger <- function(X.model, new_data) {
  predict(X.model, new_data)$predictions[,2]
}

custom_predict_rpart <- function(X.model, new_data) {
  predict(X.model, new_data)[,2]
}

fl_ranger <- flashlight(model = ranger_model,  label = "Titanic Ranger",
                 metrics = list(auc = AUC), predict_function = custom_predict_ranger)

fl_rpart <- flashlight(model = tree_model,  label = "Titanic Tree",
                 metrics = list(auc = AUC), predict_function = custom_predict_rpart)

fl <- multiflashlight(list(fl_ranger, fl_rpart), data = titanic_imputed, y = "survived")

pvp <- light_profile(fl, v = "fare", type = "predicted")
plot(pvp)
```

## Response profile 

```{r}
custom_predict <- function(X.model, new_data) {
  predict(X.model, new_data)$predictions[,2]
}
fl <- flashlight(model = ranger_model, data = titanic_imputed, y = "survived", label = "Titanic Ranger",
                 metrics = list(auc = AUC), predict_function = custom_predict)

pvp <- light_profile(fl, v = "fare", type = "response")
plot(pvp)
```

## Residual profile - One model

```{r}
custom_predict <- function(X.model, new_data) {
  predict(X.model, new_data)$predictions[,2]
}
fl <- flashlight(model = ranger_model, data = titanic_imputed, y = "survived", label = "Titanic Ranger",
                 metrics = list(auc = AUC), predict_function = custom_predict)

rvp <- light_profile(fl, v = "fare", type = "residual")
plot(rvp)
```

## Residual profile - Two models

```{r}
custom_predict_ranger <- function(X.model, new_data) {
  predict(X.model, new_data)$predictions[,2]
}

custom_predict_rpart <- function(X.model, new_data) {
  predict(X.model, new_data)[,2]
}

fl_ranger <- flashlight(model = ranger_model,  label = "Titanic Ranger",
                 metrics = list(auc = AUC), predict_function = custom_predict_ranger)

fl_rpart <- flashlight(model = tree_model,  label = "Titanic Tree",
                 metrics = list(auc = AUC), predict_function = custom_predict_rpart)

fl <- multiflashlight(list(fl_ranger, fl_rpart), data = titanic_imputed, y = "survived")

rvp <- light_profile(fl, v = "fare", type = "residual")
plot(rvp)
```

## Global surrogate model

```{r}
custom_predict <- function(X.model, new_data) {
  predict(X.model, new_data)$predictions[,2]
}
fl <- flashlight(model = ranger_model, data = titanic_imputed, y = "survived", label = "Titanic Ranger",
                 metrics = list(auc = AUC), predict_function = custom_predict)

surr <- light_global_surrogate(fl)
plot(surr)

```

# Predict Parts

## BreakDown

```{r}
custom_predict <- function(X.model, new_data) {
  predict(X.model, new_data)$predictions[,2]
}
fl <- flashlight(model = ranger_model, data = titanic_imputed, y = "survived", label = "Titanic Ranger",
                 metrics = list(auc = AUC), predict_function = custom_predict)

bd <- light_breakdown(fl, new_obs = titanic_imputed[1, ], n_max = 1000)
plot(bd)

```

# Predict Profile

## ICE - One model

```{r}
custom_predict <- function(X.model, new_data) {
  predict(X.model, new_data)$predictions[,2]
}
fl <- flashlight(model = ranger_model, data = titanic_imputed, y = "survived", label = "Titanic Ranger",
                 metrics = list(auc = AUC), predict_function = custom_predict)

cp <- light_ice(fl, v = "fare", seed = 123, n_max = 200)
plot(cp)

```

## ICE - Two models

```{r}
custom_predict_ranger <- function(X.model, new_data) {
  predict(X.model, new_data)$predictions[,2]
}

custom_predict_rpart <- function(X.model, new_data) {
  predict(X.model, new_data)[,2]
}

fl_ranger <- flashlight(model = ranger_model,  label = "Titanic Ranger",
                 metrics = list(auc = AUC), predict_function = custom_predict_ranger)

fl_rpart <- flashlight(model = tree_model,  label = "Titanic Tree",
                 metrics = list(auc = AUC), predict_function = custom_predict_rpart)

fl <- multiflashlight(list(fl_ranger, fl_rpart), data = titanic_imputed, y = "survived")

cp <- light_ice(fl, v = "fare", seed = 123, n_max = 200)
plot(cp)
```