---
title: "flashlight"
author: "Szymon Maksymiuk"
date: "05 08 2020"
output:
  html_document:
    toc: true
    toc_float: true
---
  
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE, warning = FALSE)
```



Load [`titanic_imputed`](https://modeloriented.github.io/DALEX/reference/titanic.html) data set.

```{r}
data(titanic_imputed, package = "DALEX")

head(titanic_imputed)
```

```{r}
library(flashlight)
library(MetricsWeighted)
```


Fit a forest type model and decision tree to the titanic imputed data. 

```{r}
ranger_model <- ranger::ranger(survived~., data = titanic_imputed, classification = TRUE, probability = TRUE)
tree_model <- rpart::rpart(as.factor(survived)~., data = titanic_imputed)
```

# Model Parts

## Permutation feature importance - One model

```{r}
custom_predict <- function(X.model, new_data) {
  predict(X.model, new_data)$predictions[,1]
}
fl <- flashlight(model = ranger_model, data = titanic_imputed, y = "survived", label = "Titanic Ranger",
                 metrics = list(auc = AUC), predict_function = custom_predict)
imp <- light_importance(fl, m_repetitions = 10)
plot(imp, fill = "darkred")
```

## Permutation feature importance - Two models

```{r}
custom_predict_ranger <- function(X.model, new_data) {
  predict(X.model, new_data)$predictions[,1]
}

custom_predict_rpart <- function(X.model, new_data) {
  predict(X.model, new_data)[,1]
}

fl_ranger <- flashlight(model = ranger_model,  label = "Titanic Ranger",
                 metrics = list(auc = AUC), predict_function = custom_predict_ranger)

fl_rpart <- flashlight(model = tree_model,  label = "Titanic Tree",
                 metrics = list(auc = AUC), predict_function = custom_predict_rpart)

fl <- multiflashlight(list(fl_ranger, fl_rpart), data = titanic_imputed, y = "survived")

imp <- light_importance(fl, m_repetitions = 10)
plot(imp, fill = "darkred")
```
## Interactions - One model

```{r}
custom_predict <- function(X.model, new_data) {
  predict(X.model, new_data)$predictions[,1]
}
fl <- flashlight(model = ranger_model, data = titanic_imputed, y = "survived", label = "Titanic Ranger",
                 metrics = list(auc = AUC), predict_function = custom_predict)
st_1 <- light_interaction(fl, seed = 123)
plot(st_1, fill = "darkred")
```

## Interactions - TWo model

```{r}
custom_predict_ranger <- function(X.model, new_data) {
  predict(X.model, new_data)$predictions[,1]
}

custom_predict_rpart <- function(X.model, new_data) {
  predict(X.model, new_data)[,1]
}

fl_ranger <- flashlight(model = ranger_model,  label = "Titanic Ranger",
                 metrics = list(auc = AUC), predict_function = custom_predict_ranger)

fl_rpart <- flashlight(model = tree_model,  label = "Titanic Tree",
                 metrics = list(auc = AUC), predict_function = custom_predict_rpart)

fl <- multiflashlight(list(fl_ranger, fl_rpart), data = titanic_imputed, y = "survived")

st_2 <- light_interaction(fl, seed = 123)
plot(st_2, fill = "darkred")
```


## Pairwise Interactions - One model

```{r}
custom_predict <- function(X.model, new_data) {
  predict(X.model, new_data)$predictions[,1]
}
fl <- flashlight(model = ranger_model, data = titanic_imputed, y = "survived", label = "Titanic Ranger",
                 metrics = list(auc = AUC), predict_function = custom_predict)
stp <- light_interaction(fl, seed = 123, v = most_important(st_1, 4), pairwise = TRUE)
plot(stp, fill = "darkred")
```

## Interactions - TWo model

```{r}
custom_predict_ranger <- function(X.model, new_data) {
  predict(X.model, new_data)$predictions[,1]
}

custom_predict_rpart <- function(X.model, new_data) {
  predict(X.model, new_data)[,1]
}

fl_ranger <- flashlight(model = ranger_model,  label = "Titanic Ranger",
                 metrics = list(auc = AUC), predict_function = custom_predict_ranger)

fl_rpart <- flashlight(model = tree_model,  label = "Titanic Tree",
                 metrics = list(auc = AUC), predict_function = custom_predict_rpart)

fl <- multiflashlight(list(fl_ranger, fl_rpart), data = titanic_imputed, y = "survived")

stp <- light_interaction(fl, seed = 123, v = most_important(st_2, 4), pairwise = TRUE)
plot(stp, fill = "darkred")
```


# Model Profile

## ALE Plot - One model


```{r}
custom_predict <- function(X.model, new_data) {
  predict(X.model, new_data)$predictions[,1]
}
fl <- flashlight(model = ranger_model, data = titanic_imputed, y = "survived", label = "Titanic Ranger",
                 metrics = list(auc = AUC), predict_function = custom_predict)

ale <- light_profile(fl, v = "fare", type = "ale")
plot(ale)
```
## ALE Plot - Two models


```{r}
custom_predict_ranger <- function(X.model, new_data) {
  predict(X.model, new_data)$predictions[,1]
}

custom_predict_rpart <- function(X.model, new_data) {
  predict(X.model, new_data)[,1]
}

fl_ranger <- flashlight(model = ranger_model,  label = "Titanic Ranger",
                 metrics = list(auc = AUC), predict_function = custom_predict_ranger)

fl_rpart <- flashlight(model = tree_model,  label = "Titanic Tree",
                 metrics = list(auc = AUC), predict_function = custom_predict_rpart)

fl <- multiflashlight(list(fl_ranger, fl_rpart), data = titanic_imputed, y = "survived")

ale <- light_profile(fl, v = "fare", type = "ale")
plot(ale)
```

## Partial Dependence Plot - One model

```{r}
custom_predict <- function(X.model, new_data) {
  predict(X.model, new_data)$predictions[,2]
}
fl <- flashlight(model = ranger_model, data = titanic_imputed, y = "survived", label = "Titanic Ranger",
                 metrics = list(auc = AUC), predict_function = custom_predict)

pdp <- light_profile(fl, v = "fare", type = "partial dependence")
plot(pdp)
```

## Partial Dependence Plot - Two models

```{r}
custom_predict_ranger <- function(X.model, new_data) {
  predict(X.model, new_data)$predictions[,2]
}

custom_predict_rpart <- function(X.model, new_data) {
  predict(X.model, new_data)[,1]
}

fl_ranger <- flashlight(model = ranger_model,  label = "Titanic Ranger",
                 metrics = list(auc = AUC), predict_function = custom_predict_ranger)

fl_rpart <- flashlight(model = tree_model,  label = "Titanic Tree",
                 metrics = list(auc = AUC), predict_function = custom_predict_rpart)

fl <- multiflashlight(list(fl_ranger, fl_rpart), data = titanic_imputed, y = "survived")

pdp <- light_profile(fl, v = "fare", type = "partial dependence")
plot(pdp)
```
## Predicted value profile - One model

```{r}
custom_predict <- function(X.model, new_data) {
  predict(X.model, new_data)$predictions[,2]
}
fl <- flashlight(model = ranger_model, data = titanic_imputed, y = "survived", label = "Titanic Ranger",
                 metrics = list(auc = AUC), predict_function = custom_predict)

pvp <- light_profile(fl, v = "fare", type = "predicted")
plot(pvp)
```

## Predicted value profile - Two models

```{r}
custom_predict_ranger <- function(X.model, new_data) {
  predict(X.model, new_data)$predictions[,2]
}

custom_predict_rpart <- function(X.model, new_data) {
  predict(X.model, new_data)[,2]
}

fl_ranger <- flashlight(model = ranger_model,  label = "Titanic Ranger",
                 metrics = list(auc = AUC), predict_function = custom_predict_ranger)

fl_rpart <- flashlight(model = tree_model,  label = "Titanic Tree",
                 metrics = list(auc = AUC), predict_function = custom_predict_rpart)

fl <- multiflashlight(list(fl_ranger, fl_rpart), data = titanic_imputed, y = "survived")

pvp <- light_profile(fl, v = "fare", type = "predicted")
plot(pvp)
```

## Response profile 

```{r}
custom_predict <- function(X.model, new_data) {
  predict(X.model, new_data)$predictions[,2]
}
fl <- flashlight(model = ranger_model, data = titanic_imputed, y = "survived", label = "Titanic Ranger",
                 metrics = list(auc = AUC), predict_function = custom_predict)

pvp <- light_profile(fl, v = "fare", type = "response")
plot(pvp)
```

## Residual profile - One model

```{r}
custom_predict <- function(X.model, new_data) {
  predict(X.model, new_data)$predictions[,2]
}
fl <- flashlight(model = ranger_model, data = titanic_imputed, y = "survived", label = "Titanic Ranger",
                 metrics = list(auc = AUC), predict_function = custom_predict)

rvp <- light_profile(fl, v = "fare", type = "residual")
plot(rvp)
```

## Residual profile - Two models

```{r}
custom_predict_ranger <- function(X.model, new_data) {
  predict(X.model, new_data)$predictions[,2]
}

custom_predict_rpart <- function(X.model, new_data) {
  predict(X.model, new_data)[,2]
}

fl_ranger <- flashlight(model = ranger_model,  label = "Titanic Ranger",
                 metrics = list(auc = AUC), predict_function = custom_predict_ranger)

fl_rpart <- flashlight(model = tree_model,  label = "Titanic Tree",
                 metrics = list(auc = AUC), predict_function = custom_predict_rpart)

fl <- multiflashlight(list(fl_ranger, fl_rpart), data = titanic_imputed, y = "survived")

rvp <- light_profile(fl, v = "fare", type = "residual")
plot(rvp)
```

## Global surrogate model

```{r}
custom_predict <- function(X.model, new_data) {
  predict(X.model, new_data)$predictions[,2]
}
fl <- flashlight(model = ranger_model, data = titanic_imputed, y = "survived", label = "Titanic Ranger",
                 metrics = list(auc = AUC), predict_function = custom_predict)

surr <- light_global_surrogate(fl)
plot(surr)

```

# Predict Parts

## BreakDown

```{r}
custom_predict <- function(X.model, new_data) {
  predict(X.model, new_data)$predictions[,2]
}
fl <- flashlight(model = ranger_model, data = titanic_imputed, y = "survived", label = "Titanic Ranger",
                 metrics = list(auc = AUC), predict_function = custom_predict)

bd <- light_breakdown(fl, new_obs = titanic_imputed[1, ], n_max = 1000)
plot(bd)

```

# Predict Profile

## ICE - One model

```{r}
custom_predict <- function(X.model, new_data) {
  predict(X.model, new_data)$predictions[,2]
}
fl <- flashlight(model = ranger_model, data = titanic_imputed, y = "survived", label = "Titanic Ranger",
                 metrics = list(auc = AUC), predict_function = custom_predict)

cp <- light_ice(fl, v = "fare", seed = 123, n_max = 200)
plot(cp)

```

## ICE - Two models

```{r}
custom_predict_ranger <- function(X.model, new_data) {
  predict(X.model, new_data)$predictions[,2]
}

custom_predict_rpart <- function(X.model, new_data) {
  predict(X.model, new_data)[,2]
}

fl_ranger <- flashlight(model = ranger_model,  label = "Titanic Ranger",
                 metrics = list(auc = AUC), predict_function = custom_predict_ranger)

fl_rpart <- flashlight(model = tree_model,  label = "Titanic Tree",
                 metrics = list(auc = AUC), predict_function = custom_predict_rpart)

fl <- multiflashlight(list(fl_ranger, fl_rpart), data = titanic_imputed, y = "survived")

cp <- light_ice(fl, v = "fare", seed = 123, n_max = 200)
plot(cp)
```