---
title: "kknn"
date: "`r format(Sys.time(), '%d-%m-%Y')`"
output:
  html_document:
    toc: true
    toc_float: true
---
  
This report aims to present the capabilities of the package `kknn` in the field of k-Nearest Neighbor galss-box models.

The document contains a use-case of on the [titanic_imputed](https://modeloriented.github.io/DALEX/reference/titanic.html) data set described in Section real-world use-case of the article.

Please note that the examples may be incomplete. If you think something is missing, feel free to make a pull request at the GitHub repository [MI2DataLab/IML-tools](https://github.com/MI2DataLab/IML-tools)

The document is a part of the paper "Landscape of R packages for Explainable Machine Learning", S. Maksymiuk, A. Gosiewska, and P. Biecek. 
The list of use-cases for all packages included in the article is [here](https://mi2datalab.github.io/IML-tools/).  

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE, warning = FALSE)
```



Load [`titanic_imputed`](https://modeloriented.github.io/DALEX/reference/titanic.html) data set.

```{r}
data(titanic_imputed, package = "DALEX")
titanic_imputed$survived <- as.factor(titanic_imputed$survived)

head(titanic_imputed)
```

```{r}
library("kknn")
```


Fit a rules type model to the titanic imputed data.

```{r}
model <- kknn(survived~., titanic_imputed, titanic_imputed)
```


# Matrix of indices of the K nearest neighbours 


```{r}
model$C[1:15,]
```

# Matrix of distances of the K nearest neighbours 

```{r}
# we round the values so they will print in a nice way
round(model$D[1:15,], 6)
```