---
title: "modelDown"
date: "`r format(Sys.time(), '%d-%m-%Y')`"
output:
  html_document:
    toc: true
    toc_float: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE, warning = FALSE)
```

Load [`titanic_imputed`](https://modeloriented.github.io/DALEX/reference/titanic.html) data set.

```{r}
data(titanic_imputed, package = "DALEX")

head(titanic_imputed)
```


```{r}
library(DALEX)
library(modelDown)
library(randomForest)

set.seed(123)
```

Fit a random forest and logistic regression to the titanic imputed data.

```{r}
rf_model <- randomForest(survived~., data = titanic_imputed)
glm_model <- glm(survived~., data = titanic_imputed)
```


# Generate

```{r}
explainer_rf <- DALEX::explain(rf_model,
                        data = titanic_imputed[, -8], y = titanic_imputed[, 8], verbose = FALSE)
modelDown(explainer_rf, output_folder = "modelDown")
```

modelDown for models comparison.


```{r}
explainer_rf <- DALEX::explain(rf_model,
                        data = titanic_imputed[, -8], y = titanic_imputed[, 8], verbose = FALSE)
explainer_glm <- DALEX::explain(glm_model,
                        data = titanic_imputed[, -8], y = titanic_imputed[, 8], verbose = FALSE)
modelDown(explainer_rf, explainer_glm, output_folder = "modelDown_2_models")

```


The generated modelDown reports are is avialible at: [https://mi2datalab.github.io/IML-tools/modelDown/index.html](https://mi2datalab.github.io/IML-tools/modelDown/index.html) and [https://mi2datalab.github.io/IML-tools/modelDown_2_model/index.html](https://mi2datalab.github.io/IML-tools/modelDown_2_model/index.html)

modelDown provides various explanation methods listed below as headers.



# Model parts

## Variable importance 

# Model profile

## PDP

## ALE

# Model diagnostics

## Cumulative distribution of residuals

## Boxplot of residuals





