---
title: "modelStudio"
date: "`r format(Sys.time(), '%d-%m-%Y')`"
output:
  html_document:
    toc: true
    toc_float: true
---

  
This report aims to present the capabilities of the package `modelStudio`. 

The document contains a use-case of on the [titanic_imputed](https://modeloriented.github.io/DALEX/reference/titanic.html) data set described in Section real-world use-case of the article.

We did our best to show the entire range of the implemented explanations. Please note that the examples may be incomplete. If you think something is missing, feel free to make a pull request at the GitHub repository [MI2DataLab/IML-tools](https://github.com/MI2DataLab/IML-tools)

The document is a part of the paper "Landscape of R packages for ExplainableMachine Learning", S. Maksymiuk, A. Gosiewska, and P. Biecek. 
The list of use-cases for all packages included in the article is [here](https://mi2datalab.github.io/IML-tools/).  

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE, warning = FALSE)
```

Load [`titanic_imputed`](https://modeloriented.github.io/DALEX/reference/titanic.html) data set.

```{r}
data(titanic_imputed, package = "DALEX")

head(titanic_imputed)
```


```{r}
library(DALEX)
library(modelStudio)

set.seed(123)
```

Fit a random forest and logistic regression to the titanic imputed data.

```{r}
rf_model <- ranger::ranger(survived~., data = titanic_imputed, classification = TRUE, probability = TRUE)
```

# Report

```{r}
explainer_rf <- DALEX::explain(rf_model,
                        data = titanic_imputed[, -8], y = titanic_imputed[, 8], verbose = FALSE)
ms <- modelStudio(explainer_rf, B = 50)
r2d3::save_d3_html(ms, file = "./modelStudio_titanic.html")
```

The generated modelStudio is avialible at: [https://mi2datalab.github.io/IML-tools/modelStudio_titanic.html](https://mi2datalab.github.io/IML-tools/modelStudio_titanic.html) 

ModelStudio provides various explanation methods listed below as headers.

# Model parts

## Permutational variable importance

# Model profile

## PDP

## ALE

# Predict parts

## SHAP

## Break Down

# Predict Profile

## Ceteris Paribus










