---
title: "modelStudio"
date: "`r format(Sys.time(), '%d-%m-%Y')`"
output:
  html_document:
    toc: true
    toc_float: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE, warning = FALSE)
```

Load [`titanic_imputed`](https://modeloriented.github.io/DALEX/reference/titanic.html) data set.

```{r}
data(titanic_imputed, package = "DALEX")

head(titanic_imputed)
```


```{r}
library(DALEX)
library(modelStudio)

set.seed(123)
```

Fit a random forest and logistic regression to the titanic imputed data.

```{r}
rf_model <- ranger::ranger(survived~., data = titanic_imputed, classification = TRUE, probability = TRUE)
```

# Report

```{r}
explainer_rf <- DALEX::explain(rf_model,
                        data = titanic_imputed[, -8], y = titanic_imputed[, 8], verbose = FALSE)
ms <- modelStudio(explainer_rf, B = 50)
r2d3::save_d3_html(ms, file = "./modelStudio_titanic.html")
```

The generated modelStudio is avialible at: [https://mi2datalab.github.io/IML_tools/modelStudio_titanic.html](https://mi2datalab.github.io/IML_tools/modelStudio_titanic.html) 

ModelStudio provides various explanation methods listed below as headers.

# Model parts

## Permutational variable importance

# Model profile

## PDP

## ALE

# Predict parts

## SHAP

## Break Down

# Predict Profile

## Ceteris Paribus










